---
title: "Homework 2"
author: "Annie Yu"
UNI: "xy2404"
date: "10/3/2018"
output: github_document
---

```{r, echo = FALSE}
library(tidyverse)
```

# Problem 1:

Read and clean the data; retain line, station, name, station latitude / longitude, routes served, entry, vending, entrance type, and ADA compliance. Convert the entry variable from character (YES vs NO) to a logical variable

```{r}
NYC_transit = read_csv(file = "/Users/annie/Desktop/data science/Homework/Homework_2/NYC_Transit_Subway_Entrance_And_Exit_Data.csv") %>% 
janitor::clean_names() %>% 
select(line, station_name, station_latitude, station_longitude, starts_with("route"), entry, vending, entrance_type, ada) %>% 
mutate(entry = recode(entry, 'YES' = T, 'NO' = F)) 

dim(NYC_transit)

```
For problem 1, the dataset contains `r colnames(NYC_transit)` variables. 

Now the dataset is stored in the dataframe, which has `r nrow(NYC_transit)` rows and `r ncol(NYC_transit)` columns.

## How many distinct stations are there?

```{r}
NYC_transit %>%
 distinct(station_name, line) %>% 
 nrow()
```


## How many stations are ADA compliant?

```{r}
NYC_transit %>% 
  filter(ada == T) %>% 
  distinct(station_name, line) %>% 
  nrow()
```


## The proportion of station entrances / exits without vending allow entrance
```{r}
nrow(NYC_transit %>% filter(entry== T&vending == "NO"))/nrow(NYC_transit %>%  filter(vending =="NO"))
```
In all entrances / exits without vending, the proportion of that allow entrance is 0.377

## Reformat data so that route number and route name are distinct variables. How many distinct stations serve the A train?

```{r}
NYC_transit %>% 
  gather(key = route_number, value = route_name, route1:route11) %>% 
  filter(route_name == 'A') %>% 
  distinct(station_name, line) %>% 
  nrow()

```

## Of the stations that serve the A train, how many are ADA compliant?
```{r}
NYC_transit %>% 
  gather(key = route_number, value = route_name, route1:route11) %>%
  filter(route_name == 'A', ada == T) %>% 
  distinct(station_name, line) %>% 
  nrow()
```


# Problem 2:

## Read and clean the Mr. Trash Wheel sheet:
```{r}
Trash_wheel_data = readxl::read_xlsx("/Users/annie/Desktop/data science/Homework/Homework_2/HealthyHarborWaterWheelTotals2018-7-28.xlsx") %>%  
janitor::clean_names() %>% 
filter(!dumpster == "NA") %>% 
mutate(sports_balls = as.integer(round(sports_balls,0)))
```

## Read and clean precipitation data for 2016 and 2017

```{r}
prec_2017 =  readxl::read_xlsx("/Users/annie/Desktop/data science/Homework/Homework_2/HealthyHarborWaterWheelTotals2018-7-28.xlsx", sheet = 4, range = 'A2:B15') %>% 
  mutate(year = 'rep(2017,13)') 
```

```{r}
prec_2016 =  readxl::read_xlsx("/Users/annie/Desktop/data science/Homework/Homework_2/HealthyHarborWaterWheelTotals2018-7-28.xlsx", sheet = 5, range = 'A2:B15') %>% 
  mutate(year = 'rep(2016,13)') 
```

```{r}
prefull = rbind(prec_2017,prec_2016) %>% 
  mutate(month = as.factor(Month)) 
  levels(prefull$month) = month.name
  prefull
  
```

## What was the median number of sports balls in a dumpster in 2016?

```{r}
median(filter(Trash_wheel_data, year == 2016)$sports_balls)
```

# Problem 3  
```{r}
library(p8105.datasets)
data(brfss_smart2010)
```

Format the data to use appropriate variable names;
Focus on the “Overall Health” topic
Exclude variables for class, topic, question, sample size, and everything from lower confidence limit to  GeoLocation
Structure data so that values for Response (“Excellent” to “Poor”) are column names / variables which indicate the proportion of subjects with each response (which are values of Data_value in the original dataset)
Create a new variable showing the proportion of responses that were “Excellent” or “Very Good”
```{r}
brfss =
  brfss_smart2010 %>% 
  janitor::clean_names() %>%
  filter(topic == "Overall Health") %>% 
  select(-class, -topic, -question, -sample_size, -(confidence_limit_low:geo_location)) %>% 
  spread(key = response, value = data_value) %>% 
  janitor::clean_names() %>%
  mutate(proportion = (excellent + very_good)/ (excellent + very_good + good + fair + poor))
```

## How many unique locations are included in the dataset?
```{r}
brfss_smart2010 %>% 
distinct(Locationdesc) %>% 
nrow()

```

## How many state are included in the dataset and What state is observed the most?
```{r}
brfss_smart2010 %>%
distinct(Locationabbr) %>% 
nrow()

tail(names(sort(table(brfss_smart2010$Locationabbr))),1)
```

## In 2002, what is the median of the “Excellent” response value?

```{r}
median(brfss$excellent, na.rm = TRUE)
```


 
## Make a histogram of “Excellent” response values in the year 2002.

```{r}
ggplot(filter(brfss, year == 2002),
       aes(x = excellent)) +
         geom_histogram() +
  labs(
    title = "The histogram of “Excellent” response values in the year 2002"
  )
```

## Make a scatterplot showing the proportion of “Excellent” response values in New York County and Queens County (both in NY State) in each year from 2002 to 2010.
```{r}
ggplot(filter(brfss, locationdesc == "NY - New York County"| locationdesc == "NY - Queens County"), aes(x = year, y = excellent))+
  geom_point(aes(color= locationdesc, alpha = 0.5)) +
  labs(
    title = "The proportion of “Excellent” response values in New York County and Queens County in each year from 2002 to 2010"
  )
  
```


